Evaluating isolation and contact tracing to control pandemic potential influenza outbreaks

### 2025-05-15 inst/paper/main.tex
add results and figure for max weekly cases

>>>>

Contact tracing systems have a capacity limit which if exceeded will lower ascertainment of case contacts. The infinite susceptible population assumption in our model means uncontrolled outbreaks and contacts requiring tracing can become infinitely large. However, we find that in the early acute phase of both contained and uncontained epidemics the maximum weekly cases exceeds 600 in some scenarios (Figure \ref{fig:max-weekly-cases}). These cases and their contacts require testing and potentially isolating, showing the rapid speed at which outbreaks can overburden surveillance systems. The fact that some outbreaks have more maximum weekly case than the outbreak limit we define shows that outbreaks can become almost impossible to control on the scale of weeks from the initial cases (Figure \ref{fig:max-weekly-cases}). When isolation and 100\% of contacts are traced in the most optimal isolation response scenario (LFT) the maximum number of cases weekly is around 450 ($R = 3.5$). \\

\begin{figure}[ht]
\centering
\includegraphics[width=\textwidth]{../plots/max_weekly_cases.png}
\caption{Max...}
\label{fig:max-weekly-cases}
\end{figure}
